\documentclass{emulateapj}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{float}
%\usepackage{float}

\def\prd{Phys. Rev. D}

\def\jcap{J. Cosmology Astropart. Phys.}
                % Journal of Cosmology and Astroparticle Physics

\def\bminus{$\beta^-$}
\def\Msol{M\ensuremath{_{\odot}}}


\begin{document}

\title{Uncertainty in r-process and s-process Sites}

\author{Joshua Wallace}
\affil{AST 514, Department of Astrophysical Sciences, Princeton
  University, Princeton, NJ 08544}

\begin{abstract}
Both the r- and s-process are important for
producing nuclides heavier than $^{56}$Fe.  A brief history of the
development of the r- and s-process is presented as well as the
relevant nuclear physics.  The focus of this work
is on the details of the r- and s-processes themselves, especially the
proposed sites where they are operative. Details of the processes
themselves as well as certain observations give important clues as to
what these sites might be.
  The s-process abundances consist of
2-3 components.  The main s-process
component is thought to happen during thermal flashes in low mass AGB
stars, the weak s-process component is thought to happen during core
helium burning, and the strong s-process component can be explained by
having the main s-process component operate in stars with low
metallicity.  The nature of the r-process strongly suggests that it
operates in transient phenomena.  Strongest candidates for the site of the r-process consist of proto-neutron star
winds and binary neutron star mergers.  These proposed sites are
investigated.
\end{abstract}

\keywords{nuclear reactions, nucleosynthesis, abundances}


\section{Introduction}
\input{intro.tex}

\section{History of Development of Nucleosynthesis}
\input{history.tex}

\section{The Physics Behind Nucleosynthesis}
\input{nucleosynthesis.tex}

\section{s-process}

\input{s.tex}

\section{r-process}

\input{r.tex}

\section{Conclusion}
\input{conclusion.tex}

\bibliographystyle{apj}
\bibliography{bibliography}

\end{document}
